Triptych: logarithmic-sized linkable ring signatures with applications

### 2020-08-26 paper/iacr.tex
Fix paper notation

The user generates $W$ auxiliary commitments $P'_u \equiv \com(a_u,s'_u)$ to the same amounts, but with different masks $\{s'_u\}$ chosen uniformly at random from $\F$.
Then, the user generates $W$ spend proofs, each using the following prover inputs for $u \in [0,W)$:
$$\mathcal{P}_{par}(\{M_{i,\alpha}\},r_u^{-1}U;(l_u,\{r_u,s_u-s'_u\}))$$

>>>>

The user generates $W$ auxiliary commitments $P'_u \equiv \com(a_u,s'_u)$ to the same amounts, but with different masks $\{s'_u\}$ chosen uniformly at random from $\F$.
Then, the user generates $W$ spend proofs, each using the following prover inputs for $u \in [0,W)$:
$$\mathcal{P}_{par}(\{M_{k,0}\}_{k=0}^{N-1},\{M_{k,1}-P'_u\}_{k=0}^{N-1},r_u^{-1}U;(l_u,r_u,s_u-s'_u))$$
